Universal Anonymous Signatures

### 2022-07-15 prism-backend/research/gsac/formal-uas.tex
Some deep syntax re-writing.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given \parm, returns a user's secret
  key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential \cred from an issuer in the system, on attribute
  set $\attrs$. The user leverages a set of credentials \scred, each with a
  matching issuer key in \sipk (ommitted in \Obtain for readability). The user
  outputs the produced credential \cred, while the issuer outputs the protocol
  transcript \utrans for the produced credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. For readability, we assume
  that, for each $\cred \in \scred$, we can get the corresponding issuer public
  key \ipk; also, we use use \Sig to denote the tuple $(\sig,\yeval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\usk,\scred,\attrs)
  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
  \famfissue, the issuance function defines the customized conditions required
  by the issuer to grant a credential over attributes \attrs, when requested by
  a user with secret key \usk, potentially leveraging a set of previously
  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\scred,\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, credentials \scred, and message to be signed
  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
  is revealed in plaintext along with the signature, and $\yeval^1$ is
  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
  (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials used for signing, and signed message, should be extractable by an
  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, observe that the former is chosen
on a per-signature basis, probably after negotiation between signer and
verifier. As such, it governs the information revealed at signing time. On the
other hand, \finsp governs the information that may be revealed after signing.
Moreover, it is defined by openers, and even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function.

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid. In all cases, we use bold font to
denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
  user, we use $\UK[\uid]$. 
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,\scid,\siid)$, where \uid is the
  identity of the owner of the credential, \cred (when available) is the
  credential itself, \iid is the identifier of the credential issuer, \attrs
  are the attributes included in \cred, \scid are the identifiers of the
  credentials (if any) that \uid used to request \cred, and \siid the issuers
  of those credentials. For notational
  convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
  $\cid \in \scid$. Also, when clear from context, we sometimes use
  $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
  $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\uid,\oid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists \cid,\cid' \in \scid~\suchthat~\cid \in \CRED \land
          \cid' \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
          \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
            \Yeval,\msg,\feval$} \\          
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
          \TYeval) \\
          \pcind (\tyinsp,\tiproof) \gets
          \Open(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\cscid_b],\attrs),\adv \rangle \\
          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \cscid_b, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

>>>>

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage their keys to request credentials.
Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
these keys to request multiple credentials, then from the point of view of our
modelling, we see this \emph{cryptographically} as two different users.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
  function \fissue for checking that credential requestors meet the conditions
  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
  pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given \parm, returns a user's secret
  key.
\item[$\langle
  \Obtain(\usk,\ipk,\sCred,\attrs),
  \Issue(\isk,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the \Obtain
  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
  issuer in the system, where \cid is a unique identifier for the credential,
  \ipk is the issuer's public key and \cred is the actual credential, on
  attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
  user outputs the produced credential \Cred, while the issuer outputs the
  corresponding protocol transcript \utrans.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\fissue: (\usk,\attrs,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]})
  \rightarrow 0/1$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with secret key \usk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
  may be $0$ if no previously obtained credential is used). \fissue returns $1$
  to accept a request, $0$ to reject it.
\item[$\feval: (\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user secret key \usk, a set of credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n \ge 1$), and the message to be signed \msg. \feval outputs two values,
  $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour of
  \finsp, and must belong in a well defined set \rngfeval. For readability, we
  write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\usk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},\msg)
  \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

\feval and \finsp may seem redundant. However, the former is chosen on a
per-signature basis, probably after negotiation between signer and verifier, and
governs the information revealed at signing time. On the other hand, \finsp
governs the information that may be revealed after signing, and is defined by
openers when they set up their key pair. Thus even though signers and verifiers
may negotiate to use any opener for a given signature, it is not possible for
an opener to change the chosen function. In the sequel, we restrict to
\UAS-acceptable functions, which we will also use to give \CUASGen restrictions.
Both concepts are defined next.

\begin{definition}{(\UAS-acceptable functions)}
  \label{def:uas-acc-func}
  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
  is one-way with respect to \usk. That is, given the output of \fissue
  (similarly, \feval or \finsp), it is at least computationally unfeasible to
  recover the \usk value used to produce it.
\end{definition}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
for issuers, \iid; and for openers, \oid. % In all cases, we use bold font to
% denote sets: e.g., \scid and \siid denote sets of credential and issuer
% identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of honest users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.
\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
  track of corrupt users/issuers/openers. They are sets of
  {\uid}s/{\iid}s/{\oid}s.    
\item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
  user, we use $\UK[\uid]$. 
\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
  use \PUBIK to refer to the public component, which also includes the \fissue
  function; and \PRVIK refers to the private component of the key pair.
\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
  of \fissue, \OK includes the \finsp function.
\item[\CRED.] Stores information related to credentials obtained by users in
  the system. Thus, it is indexable by \cid. More specifically, it stores
  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
  credential, \cred (when available) is the credential itself, \iid is the
  identifier of the credential issuer, \attrs are the attributes included in
  \cred, $n$ is the number of credentials used to support this request, and
  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
  identifiers. For notational convenience, we may use $\CRED[\scid]$
  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
  issuance anonymity game.
\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
  same \uid.
\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
  the opener, \scid is the set of identifiers of the credentials used for
  signing, \feval is the signing evaluation function, and \sig and \msg are the
  produced signature and signed message.
\item[\CSIG.] Maintains challenge signatures output to the adversary in the
  signature anonymity game, and is indexable by challenge signatures \csig.
  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
  user  and credential identifiers set used to produce \csig; as well as the
  corresponding challenge user and credential set indexed by the complementary
  $1-b$; the signed message \msg and signing evaluation function \feval, the
  result of \feval, \Yeval, and the opener identifier \oid.
\end{description}

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i \in [n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \Cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{[n]}],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{[n]}],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid=\lbrace \iid_i
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
          \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,\iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
          \feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
          \cid_j \in \CCRED: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
          \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
            \Yeval,\msg,\feval$} \\          
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
          \TYeval) \\
          \pcind (\tyinsp,\tiproof) \gets
          \Open(\PRVOK[\oid],\IK[\ISR[\scid]],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
          \rbrace_{i\in[n]})$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
          \attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,\iid_i)
          \rbrace_{i\in[n]}) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
          \textrm{\todo{\scid notation}} \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
          \textrm{\todo{\scid notation}} \\                    
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
non-frameability. In addition, we define two auxiliary properties for defining
the expected behaviour of the \ExtractIssue and \ExtractSign functions.
\todo{The following may need to be moved elsewhere and/or re-written.}
For instance, the extraction type are used in
\cite{lnpy21,nps22}, and functions of the identify type are used in
\cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
these techniques when there is no traditional notion of opening. Since, mostly
the unforgeability and non-frameability properties build on the extractability
and identifiability ones, we define them first. Then, we proceed with the usual
notions.

% \todo{Maybe do some drawing of the cred tree.}
